%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Jay Vo} \\ \vspace{1pt}
    \small 513-837-6970 $|$ \href{mailto:x@x.com}{\underline{duong.kej@gmail.com}} $|$ 
    \href{https://linkedin.com/in/duonghvo}{\underline{linkedin.com/in/duonghvo/}} $|$
    \href{https://github.com/duong-vo}{\underline{github.com/duong-vo}}
\end{center}





%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Engineer Intern}{May 2023 -- Nov 2023}
      {Rakuna}{}
      \resumeItemListStart
        \resumeItem{Collaborated cross-functionally to refine Rakuna's Candidate Relation Management product, which has been supporting 600+ firms with scaling their recruiting activities.}
        \resumeItem{Utilized Sidekiq for asynchronous processing of email marketing campaign initiations, achieving an 80\% reduction in emails processing and validation delays.}
        \resumeItem{Leveraged RSpec in Ruby to implement comprehensive unit and integration tests, achieving over 95\% code     coverage, ensuring the reliability and functionality of the software.}
    \resumeItemListEnd

    \resumeSubheading
      {Software Engineer Intern}{May 2022 -- Mar 2023}
      {CodeLynx}{}
      \resumeItemListStart
        \resumeItem{Partnered with a senior developer to develop a full-stack code development notebook with Clojure and React.js.}
        \resumeItem{Implemented a high-performing tree parser and the evaluator using Clojure for interpreted languages, reducing code run-time by 50\%.}
        \resumeItem{Utilized state caching on the frontend to optimize code evaluation, ensuring a smooth notebook experience for users.}
        \resumeItem{Organized the code and documented the repository for smooth launch into open source and increase overall efficiency by 15\%.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Miami University, Ohio}{Oxford, OH}
      {B.S in Computer Science}{Aug 2021 -- May 2025}
      \resumeItemListStart
        \resumeItem{GPA: 3.9, President's list for 3 semesters}
        \resumeItem{Activities: Honors College, Programming Club, Eli Lilly Leadership Institute Cohort 11}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{CodeCollab} $|$ \emph{Node.js, React, TypeScript, MongoDB, SocketIO}}{}
          \resumeItemListStart
            \resumeItem{Built a collaborative code editor with Socket.IO, Node.js and React, honing real-time web development and intuitive frontend skills.}
            \resumeItem{Enabled seamless simultaneous code editing in collaborative code editor through efficient SocketIO communications, ensuring a smooth and responsive user experience.}
            \resumeItem{GitHub repository: \href{https://github.com/duong-vo/code-review-platform}{\underline{github.com/duong-vo/code-review-platform}}}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{MyKalory} $|$ \emph{Django, React, Bootstrap, MongoDB, Google Cloud, Firebase}}{}
          \resumeItemListStart
            \resumeItem{Developed a nutrition tracking app with camera-based calorie tracking using Google Vision API in a team of four.}
            \resumeItem{Utilized Bootstrap to create a visually appealing and responsive frontend for the app, enhancing the overall user experience.}
            \resumeItem{Leveraged Firebase's client-side authentication and authorization capabilities to implement secure user-specific features.}
            \resumeItem{GitHub repository: \href{https://github.com/dominhnhut01/revolutionuc2023}{\underline{github.com/dominhnhut01/revolutionuc2023}}}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{TinderHack} $|$ \emph{Node.js, React, Express, MongoDB, Firebase}} {}
          \resumeItemListStart
            \resumeItem{Worked in a team of 4 to develop the TinderHack app, facilitating quick and interactive team formation for hackathon participants.}
            \resumeItem{Developed a robust backend API with Node.js and Express, ensuring smooth and efficient data flow between the frontend and backend.}
            \resumeItem{GitHub repository: \href{https://github.com/yahuy1/mu\_mhack\_2023}{\underline{github.com/yahuy1/mu\_mhack\_2023}}}
          \resumeItemListEnd
    \resumeSubHeadingListEnd




%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Python, Java, Ruby, JavaScript, C++, Dart, SQL, HTML/CSS} \\
     \textbf{Frameworks/Libraries}{: Ruby on Rails, React.js, Node.js, Express.js, Flask, Django, Flutter, JQuery} \\
     \textbf{Technologies}{: Git, Linux, Docker, PostgreSQL, MongoDB, AWS, Google Cloud, Firebase} \\
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
